Persistence of marine populations under climate and fishing

### 2015-01-28 Writing/older_stuff/Appendix.tex
accepted all of Malin's comments, and reorganized our writing folder for clarity

\pagebreak
\subsection{MPA fluctuations \label{MPA}}
~\\After the simulations come to equilibrium, the fluctuations in total biomass per generation fluctuate more in MPAs that are larger and spaced farther apart than simulations in which the MPAs that are smaller and more closely spaced. The large MPAs have a slightly larger average population, however large MPAs here can induce fluctuations of biomass even in deterministic simulations. Thus we expect if reproduction was stochastic, large MPAs spaced far apart would be more likely to result in extinction of the population than more closely spaced, smaller MPAs. 
\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{plots/bounded_flux.pdf}
\caption{Total population biomass is on the y axis, and generation is on the x axis. These simulations were run with climate velocity $ = 0.1$, and a proportional harvest rate $= 0.08$. }
% see bounded\_flux.R for code that made this plot
\end{figure}

@@

\subsection{Re-allocation of Effort \label{effort}}
~\\Spatial shifts of harvesters in response to MPA creation can affect sustainability of the system \citep{Botsfordetal2009}. We model the two extremes of response: either that harvesting pressure that occurred in now-MPAs is reallocated outside the reservers, or harvesting inside MPAs disappears from the system with the creation of MPAs and MPAs are effectively an effort control management technique. To reallocate effort we increased quota by 50\% in outside of MPAs (see \cite{Kaplanetal2005} for similar approach).

We found no qualitative change in our results. Reallocation of effort was effectively like increasing the harvesting rate, and thus the critical harvest rate was lower than when effort was removed from the system.

\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{plots/fig3a.pdf}
\caption{Climate velocity is on the x axis, harvest rate is on the y axis. These simulations were run with effort reallocated to areas outside of MPAs. }
% see bounded\_flux.R for code that made this plot
\end{figure}

>>>>

\pagebreak
\subsection{Protected Area fluctuations \label{MPA}}
~\\After the simulations come to equilibrium, the fluctuations in total biomass per generation fluctuate more in reserves that are larger and spaced farther apart than simulations in which the reserves that are smaller and more closely spaced. The large reserves have a slightly larger average population, however large reserves here can induce fluctuations of biomass even in deterministic simulations. Thus we expect if reproduction was stochastic, large reserves spaced far apart would be more likely to result in extinction of the population than more closely spaced, smaller reserves. We find the same effect regardless of whether or not effort remains constant. 
\begin{figure}[h]
\centering
\includegraphics[width=.75\textwidth]{plots/compare_flucts.png}
\caption{Total population biomass is on the y axis, and generation is on the x axis. These simulations were run with climate velocity $ = 0.1$, and a proportional harvest rate $= 0.02$. }
% see bounded\_flux.R for code that made this plot
\end{figure}

@@
